GPU-friendly Stroke Expansion

### 2024-04-28 paper.tex
Rebase & make paper
Redo timings and primitive count measurements
The script for gathering timings had a bug, where the times were cumulative over the scenes. Now fixed. We also include Nehab in the timings.

As part of the work to add Nehab, there's a new utility to convert scenes into RVG format. It's crude (no colors, viewport is hardcoded), but sufficient for measuring timing and primitive count.

The primitive count measurements were redone, striking waves (as it triggers a Skia bug) and adding mmark-70k.

We measured the timing of our CPU implementation, generating both line and arc primitives, against Skia's stroker, which outputs a mix of straight lines and quadratic Bézier primitives. The results are shown in Figure~\ref{fig:timings}. The time shown is the total for test files from the \emph{timings} dataset of \cite{Nehab2020}, and the tolerance in all cases was 0.25. TODO: measure against other implementations.

@@

\begin{figure}
    \includegraphics[scale=0.6]{timings}
    \caption{CPU timings for stroke expansion, comparing two versions of our stroker (outputting line and arc primitives) against Skia's curve-to-curve stroker. Measured on an Apple M1 Max}
    \Description{A stacked bar chart of the timings for stroke expansion}
    \label{fig:timings}
\end{figure}

We also compared the number of primitives generated, for varying tolerance values from 1.0 to 0.001. The number of arcs generated is significantly less than the number of line primitives. The number of arcs and quadratic Bézier primitives is comparable at practical tolerances, but the count of quadratic Béziers becomes more favorable at finer tolerances. These vertical axis shows the sum of output segment counts for test files from the \emph{timings} dataset.

>>>>

We measured the timing of our CPU implementation, generating both line and arc primitives, against the Nehab and Skia strokers, which both output a mix of straight lines and quadratic Bézier primitives. The results are shown in Figure~\ref{fig:timings}. The time shown is the total for test files from the \emph{timings} dataset of \cite{Nehab2020}, and the tolerance was 0.25 when adjustable as a parameter.

@@

\begin{figure}
    \includegraphics[scale=0.6]{timings}
    \caption{CPU timings for stroke expansion, comparing two versions of our stroker (outputting line and arc primitives) against Skia's curve-to-curve stroker. Measured on an AMD 3970}
    \Description{A stacked bar chart of the timings for stroke expansion}
    \label{fig:timings}
\end{figure}

We also compared the number of primitives generated, for varying tolerance values from 1.0 to 0.001. The number of arcs generated is significantly less than the number of line primitives. The number of arcs and quadratic Bézier primitives is comparable at practical tolerances, but the count of quadratic Béziers becomes more favorable at finer tolerances. These vertical axis shows the sum of output segment counts for test files from the \emph{timings} dataset, plus mmark-70k, and omitting the \emph{waves} example\footnote{The \emph{waves} example triggers triggers Skia issue 336617138 at finer tolerance.}.
